---
title: "Regression Analytics"
author: "Avinash Ravipudi"
date: "2022-11-10"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Q1.
```{r}
set.seed(2017)
X=runif(100)*10
Y=X*4+3.45
Y=rnorm(100)*0.29*Y+Y
```
Q1a.
```{r}
plot(X,Y)
#plot(Y~X,xlab="X",ylab="Y",col="black")
```
The plot depicts a linear relationship between Y and X. The values for Y grow as X increases. We may then develop a linear model to describe Y based on X.

Q1b.
```{r}
Accuracy=lm(Y~X)
Accuracy #y=4.465 + 3.611X
summary(Accuracy)
```
Y is explained by the following equation: y = 4.465 + 3.611X. 
The accuracy of the model is.6517, or 65%.

Q1c.
```{r}
R_squared= 0.6517
sqrt(R_squared)
```
The correlation coefficient is equal to the square root of the coefficient of determination.

Q2.
```{r}
head(mtcars,10)
summary(mtcars)
```
Q2a.
Prediction by James
```{r}
James_model=lm(mtcars$hp~mtcars$wt)
summary(James_model)
```
Prediction by Chris
```{r}
chris_model=lm(mtcars$hp~mtcars$mpg)
summary(chris_model)
```
In comparison to James' viewpoint, Chris' viewpoint is "correct." Chris' model's accuracy is 0.6024, which is higher than James' model's accuracy of 0.4339.
Q2b.
```{r}
hp_model=lm(hp~cyl+mpg,data=mtcars)
predict(hp_model,data.frame(cyl=4,
                            mpg=22))
```
A automobile with four calendars and an mpg of 22 has an estimated Horse Power of 88.94.

Q3.
```{r}
options(repos = list(CRAN="http://cran.rstudio.com/"))
#install.packages('mlbench')
library(mlbench)
data(BostonHousing)
head(BostonHousing,10)
```
Q3a.
```{r}
Homes_price=lm(medv~crim+zn+ptratio+chas,data=BostonHousing)
summary(Homes_price)
```
This model is not accurate due to the Multiple R-squared (accuracy) of 0.3599.

Q3b. 

   i.The house on the Chas River is 4.58393 times more expensive. This is due to the fact that the coefficient of chas is 4.58393. If the other house costs $1,000, the Chas River similar house would cost $4,583.93.
   
   ii.The adjacent household, which has a pupil-teacher ratio of 15, is more expensive. Because the ptratio coefficient is -1.49367, raising the ptratio by one unit lowers the property price by 1.49367. The value of the home drops by (15x1493.67) $22,405.05. With a ptratio of 18, the house's value decreases by (18x1493.67) $26,886.06. The house has a ptratio of 15 and costs $4,481.01.

Q3c. Each variable is statistically significant because its p-value is less than 0.05.

Q3d. 
```{r}
anova(Homes_price)
```
Order of importance ranked 1-4 (1 = most important, 4 = least important):
  1. crim
  2. ptratio
  3. zn
  4. chas
The larger the sum squared, the more importance given to the variable.
